Higher-Order unification for free!

### 2024-04-12 paper/main.tex
sec 3.3

When variables $x$ and $y$ can occur in term $t$ we shall write
$t_{xy}$ to stress this fact. 
\todo{add notation for problem compilation}

>>>>

In \cref{sec:eta,sec:invariant1,sec:beta,sec:llam},
we use the following schema to represent the compilation of the list of \Fo{}
problems \foUnifPb into the \Ho problems \hoUnifPb. \mapStore and \linkStore are
respectively the mapping and the link store.
%
\printAlll
  {{{p_1,p_2},{p_3,p_4}}}
  {{{t_1,t_2},{t_3,t_4}}}
  {{{X_1,A_1,{{x}}},{X_2,A_2,{{y}}}}}
  {{{\eta,\Gamma,a,b}}}

We index each sub-problem, sub-mapping, sub-link with its position in the image
starting from $1$ and counting from left to right, top to bottom. For example,
$\hoUnifPb_2$ corresponds to the \Ho problem $t_3 \Ue t_4$.
The compiled version of each $\foUnifPb_i$ is represented by $\hoUnifPb_i$.

Moreover, to indicate the scope of a \Ho variable, we use that scope as
subscript of the considered variable. For example, $X_{xy}$ is the variable $X$ 
having in scope $x$ and $y$.
